Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-01 Arxiv/main.tex
Update Arxiv/main.tex

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
{\footnotesize \tableofcontents}

@@

\noindent \textbf{Sliding Property of $\hexpmech$}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

\noindent \textbf{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon', \delta)$-differential privacy in Beta-binomial system.
\end{lem}

@@

>>>>

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
{\small \tableofcontents}

@@

\subsubsection{Sliding Property of $\hexpmech$}

@@

\subsubsection{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

\subsubsection{$(\epsilon', \delta)-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon', \delta)$-differential privacy in Beta-binomial system.
\end{lem}

@@

\subsubsection{$\gamma$-Smooth Sensitivity}
\label{sec_mechs}

\begin{definition}
Given data set $\dataobs$, if a sensitivity $S(\dataobs)$ of $\dataobs$ satisfying:

For any $\adj{\dataobs}{\dataobs'}$:
\begin{equation}
\label{eq_gamma_smooth}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation}

$S(\dataobs)$ is $\gamma -$smooth sensitivity.

\begin{thm}
\label{thm_gamma_smooth}
Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.

For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:

By Equation (\ref{eq_smooth}):
\begin{equation*}
\begin{split}
S(\dataobs) 
& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
\frac{1}{S(\dataobs)} 
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
\end{split}
\end{equation*}

Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:

\begin{equation*}
\begin{split}
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
$\implies$
\begin{equation*}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation*}

Under this smooth sensitivity, we define $\hexpmech$ as:
\begin{definition}
\label{def_smoo_2}
$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
{\unomalizer{\dataobs}}.
\end{equation*}
where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
\end{definition}

\subsubsection{$\hexpmech$ $2\epsilon$ Privacy Analysis}

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $2\epsilon$-differential privacy.
\end{lem}

  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:

  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{2} \big) \\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)\\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
  $\frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2} \cdot \gamma
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
  \big)
  }\\
  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  }\\
  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

  Given $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
\end{proof}
